---
title: "Lab #1"
author: "Zahra Khoshmanesh,Gani Agadilov,Oscar Aguilar"
topic: "01"
layout: post
root: ../../../
---
##Link RStudio and git

##Build a book

* Deliverable (1): what is the last word in chapter 15? - You don't have to answer this question, if things don't work, but please answer the next one and see the next page.

The last word in chapter 15 is pseudo-class. 

* Deliverable (2): Write a paragraph on the biggest problem you encountered when you were building the book, and how you managed to solve it.

The problem that we have met when we were building the book is lacking several packages. 
In addition, we could not knit the index.Rmd file on one of our laptops. The error says that
 Introduction.rmd file cannot be read and some functions cannot be operated. The several types
 of errors showed up and we tried to solve it separately. We also installed packages from 
Git hub account that allow us to knit the index.Rmd file. Generally, there was not a big problem that  stopped from solving the problem. We followed the instructions that given on the lab page and tried to receive the html version of the book by installing all packages that require index.Rmd file.
In our view, needing to install many packages during the knitting stage was annoying. 
It is better to know the list of packages that we need befor knitting.

The list of some packages that we got errors and installed them in order to be able to knit the index file are as follows:
bookdown
emoji


##Deal with the weather (stations) ...

```{r }
knitr::opts_chunk$set(echo = TRUE)
## R-packages
library(ggplot2)
library(tidyverse)
library(readr)
library(dplyr)
library(maps)
```

## Reading Weather Station Data

In this section, we first read weather station data as follows:

```{r}
weather <- read_fwf('ushcn-v2.5-stations.txt', fwf_widths(c(2, 1, 2, 7, 9, 10, 6, 3, 31, 7, 7, 7, 3)))
## Here we categorize the elevations
weather <- weather %>% mutate(Elevation = as.factor(ifelse(X7 < 500, 1,
                                                 ifelse(500 <= X7 & X7 < 1000, 2, 
                                                        ifelse(1000 <= X7 & X7 < 1500, 3, 
                                                               ifelse(1500 <= X7 & X7 < 2000, 4, 5))))))
```

## Weahter Station Visualization

In this section, we visualize the weather stations using their longitute, latitude and elevation as follows:

```{r}
us <- map_data('state')
p <- ggplot()
p <- p + geom_polygon(data = us, aes(x = long, y = lat, group = 
                      group), colour = "white", fill = "grey")
p <- p + geom_point(data = weather, aes(x = X6, y = X5, colour = Elevation)) + theme(legend.position = "right")
p <- p + scale_color_discrete(name = 'Elevation',
                             breaks = c('1', '2', '3', '4', '5'),
                             labels = c('< 500 m', '500-1000 m', '1000-1500 m', 
                                        '1500-2000 m', '2000 m or more'))
p <- p + ggtitle('Weather Stations')
p
```


## The US map  with AK and HI having state abbreviation ID in center

```{r}
library(ggplot2)   
library(ggalt)     # coord_proj
library(albersusa) # devtools::install_github("hrbrmstr/albersusa")
library(ggthemes)  # theme_map
library(rgeos)     # centroids
library(dplyr)
#devtools::install_github("hrbrmstr/albersusa")
# composite map with AK & HI
usa_map <- usa_composite()
# calculate the centroids for each state
gCentroid(usa_map, byid=TRUE) %>% 
  as.data.frame() %>% 
  mutate(state=usa_map@data$iso_3166_2) -> centroids
# make it usable in ggplot2
usa_map <- fortify(usa_map)
gg <- ggplot()
gg <- gg + geom_map(data=usa_map, map=usa_map,
                    aes(long, lat, map_id=id),
                    color="blue", size=0.1, fill="green")
gg <- gg + geom_text(data=centroids, aes(x, y, label=state), size=2)
gg <- gg + coord_proj(us_laea_proj)
gg <- gg + theme_map()
gg
```

## Add time zone to the US map 


```{r }
# US map with time zone for every county
#install.packages("countytimezones")
library(countytimezones)
library(choroplethr)
library(choroplethrMaps)
library(ggplot2)
library(dplyr)
data(county_tzs)
example_df <- data.frame(fips = county_tzs$fips,
                         datetime = "2019-02-09 08:30")
head(example_df)
example_df <- add_local_time(df = example_df,
                             fips = example_df$fips,
                             datetime_colname = "datetime")
head(example_df)
to_plot <- example_df %>%
  select(fips, local_time) %>%
  mutate(local_time = factor(local_time)) %>%
  dplyr::rename(region = fips, value = local_time)
a <- CountyChoropleth$new(to_plot)
a$ggplot_scale <- scale_fill_brewer(type = "qual", drop = FALSE)
a$render()
```

## ... and some funny file formats



```{r}
fn <- "ftp://ftp.ncdc.noaa.gov/pub/data/ushcn/v2.5/ushcn.tavg.latest.raw.tar.gz"
download.file(fn,destfile="tmp.tar.gz")
## Here we check the contents
files <- untar("tmp.tar.gz", list = TRUE) 
## Here we count the number of files
FilesInDir<-length(files)
#number of files in the directory
FilesInDir
## Finding the temperature file for Fort Dodge, IA
## Note that, using the weather station file, we found out that 
## the code associated to Fort Dodge, IA is USH00132999
#files[which(files == './ushcn.v2.5.5.20190204/USH00132999.raw.tavg')]

index1<-match("./ushcn.v2.5.5.20190210/USH00132977.raw.tavg",files)
index1

## From the above, we see that the 300th file from the downloaded folder is the 
## one that contains the temperature information associated to Fort Dodge, IA.




#finding the related file from the csv file with using sql command
#first install sqldf package
library(sqldf)
#install.packages('sqldf')
# extract the value of coulumn 1 to 4 related to a row having "fort dofge"
#first execute related chunk having weather dataframe or table
namesql<-sqldf("select X1,X2,X3,X4 from weather where X9 LIKE '%FORT DODGE%'")
library(stringr)
#paste all value of related x1 to x4 in 1 variable named namefile, this variable having the name of file we are interested
namefile<-str_c(namesql, collapse = "")
namefile
index1<-match("./ushcn.v2.5.5.20190210/USH00132977.raw.tavg",files)
index1



```
